\textsf{Are large language models superhuman chemists?}

### 2024-10-27 src/tex/appendix.tex
try to make compile work

\begin{table}
    \centering
    \small
    \caption{\textbf{Examples of topics evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly.} The table displays the percentage of questions in the corpus for each topic, along with example questions and the percentage of questions that were not answered correctly by the models.}
    \label{tab:chembench_corpus_models_failed_topic}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            \multicolumn{1}{c}{\textbf{Analytical Questions} 166 Questions (5.8\%) (26.5\%)} \\
            \midrule
            Which of the following methods can be used to support the structure elucidation of planar molecules by examining the topography of individual molecules? \\
            A. DESI-mass spectrometry \\
            B. XPS \\
            C. atomic force microscopy \\
            D. scanning tunneling microscopy \\
            E. secondary ion mass spectrometry \\
            \midrule
            \multicolumn{1}{c}{\textbf{Chemical Preference} 1001 Questions (35\%) (8.5\%)} \\
            \midrule
            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
            [START\_SMILES]N\#Cc1ccc(OCCCN2CC3CN\-(CCNS(=O)(=O)c4ccc(F)cc4)CC(C2)O3)cc1\-[END\-\_SMILES] \\
            [START\_SMILES]O=C1CC(c2ccc(CC(NS(=O)\-(=O)\-c3cc(Cl)cc(Cl)c3)c3nc4ccccc4[nH]3)cc2)S\-(=O)\-(=O)N1[END\_SMILES] \\
            \midrule
            \multicolumn{1}{c}{\textbf{General Chemistry} 152 Questions (5.3\%) (3.2\%)} \\
            \midrule
            Why \ce{SCl6} does not exist if other similar molecules such as \ce{SF6} exist? \\
            A. \ce{SCl6} does not exist because of steric effects \\
            B. \ce{SCl6} does not exist because of the high electronegativity of chlorine \\
            C. \ce{SCl6} does not exist because of the high ionization potential of the chlorine \\
            D. \ce{SF6} exist because of the high electronegativity of fluorine \\
            \midrule
            \multicolumn{1}{c}{\textbf{Inorganic Chemistry} 94 Questions (3.3\%) (4.2\%)} \\
            \midrule
            What is the spin-only magnetic moment (in units of Bohr-magnetons) for the low-spin case of the metal complex \ce{RhCl(CO)(PPh3)2}?\\
            \midrule
            \multicolumn{1}{c}{\textbf{Materials Science} 89 Questions (3.1\%) (0.9\%)} \\
            \midrule
            What are the conditions for the observation of effects of quantum confinement in quantum dots? \\
            A. All dimension of the material must be smaller than exciton Bohr radius \\
            B. One dimension of the quantum dot must be smaller than exciton Bohr radius \\
            C. The movement od charge carriers is limited in all spatial dimensions \\
            \midrule
            \multicolumn{1}{c}{\textbf{Organic Chemistry} 441 Questions (15.5\%) (0.5\%)} \\
            \midrule
            What makes acrylates more reactive than typical hydrocarbons? \\
            A. The carbonyl group \\
            B. The double bond \\
            C. The hydroxyl group \\
            D. The vinyl group \\
            \midrule
            \multicolumn{1}{c}{\textbf{Physical Chemistry} 179 Questions (6.3\%) (13.4\%)} \\
            \midrule
            Why are polar molecules more soluble in water than non-polar molecules? \\
            A. Non-polar molecules should break hydrogen bonds in water to dissolve \\
            B. The entropy of the system increases when non-polar molecules dissolve in water \\
            C. Water has a dipole and can easier isolate polar molecules from each other \\
            D. Water makes stable dipole-dipole interactions with polar molecules \\
            \midrule
            \multicolumn{1}{c}{\textbf{Technical Chemistry} 42 Questions (1.5\%) (4.7\%)} \\
            \midrule
            Which of the following statements is/are true about granulation shaping of solid catalysts? \\
            A. Broader product diameter distribution than pellets or extrudates \\
            B. Facilitates reactor upscaling \\
            C. It is also called snow-ball \\
            D. Not suitable to prepare egg-shell catalysts \\
            \midrule
            \multicolumn{1}{c}{\textbf{Toxicity/Safety} 690 Questions (24.2\%) (40.4\%)} \\
            \midrule
            What determines the flammability of polyols? \\
            A. Their chemical structure \\
            B. Their low volatility \\
            C. Their odor threshold \\
            D. Their reaction with acids \\
            \bottomrule
        \end{tabularx}
    }
\end{table}

>>>>

%    \caption{\textbf{Examples of topics evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly.} The table displays the percentage of questions in the corpus for each topic, along with example questions and the percentage of questions that were not answered correctly by the models.}
%    \label{tab:chembench_corpus_models_failed_topic}
%            \multicolumn{1}{c}{\textbf{Analytical Questions} 166 Questions (5.8\%) (26.5\%)} \\
%            Which of the following methods can be used to support the structure elucidation of planar molecules by examining the topography of individual molecules? \\
%            A. DESI-mass spectrometry \\
%            B. XPS \\
%            C. atomic force microscopy \\
%            D. scanning tunneling microscopy \\
%            E. secondary ion mass spectrometry \\
%            \multicolumn{1}{c}{\textbf{Chemical Preference} 1001 Questions (35\%) (8.5\%)} \\
%            \multicolumn{1}{c}{\textbf{General Chemistry} 152 Questions (5.3\%) (3.2\%)} \\
%            Why \ce{SCl6} does not exist if other similar molecules such as \ce{SF6} exist? \\
%            A. \ce{SCl6} does not exist because of steric effects \\
%            B. \ce{SCl6} does not exist because of the high electronegativity of chlorine \\
%            C. \ce{SCl6} does not exist because of the high ionization potential of the chlorine \\
%            D. \ce{SF6} exist because of the high electronegativity of fluorine \\
%            \multicolumn{1}{c}{\textbf{Inorganic Chemistry} 94 Questions (3.3\%) (4.2\%)} \\
%            What is the spin-only magnetic moment (in units of Bohr-magnetons) for the low-spin case of the metal complex \ce{RhCl(CO)(PPh3)2}?\\
%            \multicolumn{1}{c}{\textbf{Materials Science} 89 Questions (3.1\%) (0.9\%)} \\
%            What are the conditions for the observation of effects of quantum confinement in quantum dots? \\
%            A. All dimension of the material must be smaller than exciton Bohr radius \\
%            B. One dimension of the quantum dot must be smaller than exciton Bohr radius \\
%            C. The movement od charge carriers is limited in all spatial dimensions \\
%            \multicolumn{1}{c}{\textbf{Organic Chemistry} 441 Questions (15.5\%) (0.5\%)} \\
%            What makes acrylates more reactive than typical hydrocarbons? \\
%            A. The carbonyl group \\
%            B. The double bond \\
%            C. The hydroxyl group \\
%            D. The vinyl group \\
%            \multicolumn{1}{c}{\textbf{Physical Chemistry} 179 Questions (6.3\%) (13.4\%)} \\
%            Why are polar molecules more soluble in water than non-polar molecules? \\
%            A. Non-polar molecules should break hydrogen bonds in water to dissolve \\
%            B. The entropy of the system increases when non-polar molecules dissolve in water \\
%            C. Water has a dipole and can easier isolate polar molecules from each other \\
%            D. Water makes stable dipole-dipole interactions with polar molecules \\
%            \multicolumn{1}{c}{\textbf{Technical Chemistry} 42 Questions (1.5\%) (4.7\%)} \\
%            Which of the following statements is/are true about granulation shaping of solid catalysts? \\
%            A. Broader product diameter distribution than pellets or extrudates \\
%            B. Facilitates reactor upscaling \\
%            C. It is also called snow-ball \\
%            D. Not suitable to prepare egg-shell catalysts \\
%            \multicolumn{1}{c}{\textbf{Toxicity/Safety} 690 Questions (24.2\%) (40.4\%)} \\
%            What determines the flammability of polyols? \\
%            A. Their chemical structure \\
%            B. Their low volatility \\
%            C. Their odor threshold \\
%            D. Their reaction with acids \\
